Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\extraspacing {\bf Remark.} In \cite{rdr+11}, Rahul et al.\ studied the problem of storing a set $H$ of horizontal segments and a set $V$ of vertical segments in a data structure such that, given a query rectangle $r$, all the pairs $(h, v) \in H \times V$ satisfying $h \cap v \cap r \ne \emptyset$ can be reported efficiently. They developed a structure of $O(n \log n)$ space that can be built in $O(n \log n)$ time, and can be used to answer a query in $O(\log n + K)$ time, where $n = |H| + |V|$ and $K$ is the number of pairs reported. Their structure can be utilized to solve H-V 3-SJ in $O(n \log n + \out)$ time. Oh and Ahn \cite{oa19} developed a structure for a more general version of the problem; in the specific scenario of \cite{rdr+11}, the structure of \cite{oa19} matches the performance guarantees of \cite{rdr+11}. We are unaware of a way to extend their solution to handle H-V $k$-SJ of $k > 3$. Our method for proving Lemma~\ref{lmm:hv} is based on fundamentally different ideas even for $k = 3$.

>>>>

\extraspacing {\bf Remark.} In \cite{rdr+11}, Rahul et al.\ studied the problem of storing a set $H$ of horizontal segments and a set $V$ of vertical segments in a data structure such that, given a query rectangle $r$, all the pairs $(h, v) \in H \times V$ satisfying $h \cap v \cap r \ne \emptyset$ can be reported efficiently. They gave a structure of $O(n \log n)$ space that can be built in $O(n \log n)$ time and can be used to answer a query in $O(\log n + K)$ time, where $n = |H| + |V|$ and $K$ is the number of pairs reported. Their structure can be utilized to solve H-V 3-SJ in $O(n \log n + \out)$ time. Oh and Ahn \cite{oa19} developed a structure for a more general version of the problem; in the specific scenario of \cite{rdr+11}, the structure of \cite{oa19} matches the performance guarantees of \cite{rdr+11}. We are unaware of a way to extend these solutions to handle H-V $k$-SJ of $k > 3$. Our method for proving Lemma~\ref{lmm:hv} is based on drastically different ideas even for $k = 3$.
